get_artist: Get Spotify catalog information for a single artist identified by their unique Spotify ID.

?RETRY
```{r}
#Chunk 1
get_artist <- function(id,
                       authorization = get_spotify_access_token()
                       ) 
```

Insert arguments of id (The Spotify ID for an artist) and a valid access token from the Spotify Accounts service assigned to 
"authorization". Access token argument defaults to spotifyr::get_spotify_access_token()). 
get_spotify_access_token() takes environment varaibles "SPOTIFY_CLIENT_ID" assigned to "client_id" and "SPOTIFY_CLIENT_SECRET"
assigned to "client_secret".

```{r}
#Chunk 2
                       {

    base_url <- 'https://api.spotify.com/v1/artists'
```

Assign base_url to webpage that is an enpoint that stores that results of the HTTP request ?
find out what v1 means, always going to be https://api.spotify.com/v1 with something at the end.

```{r}
#Chunk 3
    params <- list(
        access_token = authorization
    )
```

Assign "params" to a list of access tokens created by the "get_spotify_access_token" from chunk 1.
Output from "authorization" is assigned to "access_token".

```{r}
#Chunk 4
    url <- str_glue('{base_url}/{id}')
```

The function "str_glue" concatenates the string values stored in base_url and id and the new 
value is assigned to the "url" variable.

```{r}
#Chunk 5
    res <- RETRY(verb = 'GET', url,
                 query = params,
                 encode = 'json',
                 terminate_on = c(401, 403, 404)
                 )
```

RETRY function is part of the httr package. RETRY takes in arguments verb, url, query, encode, and terminate_on.
Verb specifies the HTTP method used to for request (eg: 'GET', 'POST', etc.). Url was contrsucted in chunk 4. 
Query 

```{r}
    stop_for_status(res)

    res <- fromJSON(content(res, as = 'text', encoding = 'UTF-8'), flatten = TRUE)

    res
}
```