Inputs:
- Vector of characters/strings of artist ids (Spotify -> Artist -> Three Dots -> Share -> Copy Link to Artist -> after / and before ?)
- access token (Spotify Developers -> Create App -> Client ID and Client Secret)

Return:
- Violin Plot with Artists on X axis as categorical variables and Danceability (numerical value given by Spotify API) of their top tracks (usually 10 songs) on the Y-Axis;
```{r}
create_violin_plot_artist_danceability <- function(artist_ids, authorization = get_spotify_access_token()) {
    # Get top 10 tracks of artist:
    list_df_artist_top_tracks <- artist_ids %>% 
                                    purrr::map(~ get_artist_top_tracks(.x))

    # From list above, pull out the song ids and make into vector:
    vector_song_ids <- list_df_artist_top_tracks %>%
                            map(~ .x %>% pull(id)) %>% 
                            unlist()

    # Vector of artist names:
    # Get artist names and duplicate them
    vector_artist_names <- artist_ids %>% 
                                map(~ rep(get_artists(.x)$name, times = nrow(get_artist_top_tracks(.x)))) %>% 
                                unlist()

    # Get track audio features of artist 10 songs:
    df_tracks <- get_track_audio_features(vector_song_ids, authorization = get_spotify_access_token()) %>% 
                    mutate(artist = vector_artist_names)
    
    if ((length(artist_ids) <= 3 & any(nchar(vector_artist_names) > 15) & any(nchar(vector_artist_names) < 30)) | (length(artist_ids) <= 5 & all(nchar(vector_artist_names) <= 15))) {
        gg <- ggplot2::ggplot(df_tracks, aes(x=artist, y=danceability))  + 
            ggplot2::geom_violin(aes(fill = artist)) + 
            labs(title = "Danceability of Artist Top Tracks", x = "Artist", y = "Danceability", fill = "Artist") + 
            theme(plot.title = element_text(hjust = 0.5))
    } 
    else {
        gg <- ggplot2::ggplot(df_tracks, aes(x=artist, y=danceability))  + 
            ggplot2::geom_violin(aes(fill = artist)) + 
            labs(title = "Danceability of Artist Top Tracks", x = "") + 
            theme(plot.title = element_text(hjust = 0.5), 
                    axis.text.x=element_blank(), 
                    axis.ticks.x=element_blank() 
                    )
    }
    plotly::ggplotly(gg)
}
```

All Code Required Beforehand:
```{r}
# install.packages("spotifyr")
# install.packages("tidyverse")
library(spotifyr)
library(tidyverse)

Sys.setenv(SPOTIFY_CLIENT_ID = 'xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx')
Sys.setenv(SPOTIFY_CLIENT_SECRET = 'xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx')

access_token <- get_spotify_access_token()

get_artist_top_tracks <- function(id,
                                  market = 'US',
                                  authorization = get_spotify_access_token(),
                                  include_meta_info = FALSE) {

    base_url <- 'https://api.spotify.com/v1/artists'

    if (!is.null(market)) {
        if (!str_detect(market, '^[[:alpha:]]{2}$')) {
            stop('"market" must be an ISO 3166-1 alpha-2 country code')
        }
    }

    params <- list(
        market = market,
        access_token = authorization
    )
    url <- str_glue('{base_url}/{id}/top-tracks')
    res <- RETRY(verb = 'GET', url, query = params, encode = 'json', terminate_on = c(401, 403, 404))
    stop_for_status(res)

    res <- fromJSON(content(res, as = 'text', encoding = 'UTF-8'), flatten = TRUE)

    if (!include_meta_info) {
        res <- res$tracks
    }

    res
}

# install.packages("httr")
# install.packages("jsonlite")
library(httr)
library(jsonlite)
```