Parameters:
    ids - A vector of Spotify album ids
    limit - Number of projects wanted to return.  Valid if between 0 and 50.  Defaults to 20
    offset - Index of first project wanted.  Defaults to 0
    authorization - access_token generated from the get_spotify_access_token() function
Return:
    A dataframe of album track information, including duration, explicitness, track id and name, track number in album, and artist name and id

```{r}
View(get_track_segments("6b8Be6ljOzmkOmFslEb23P"))
```

```{r | new get_albums_tracks}
get_albums_tracks <- function(ids, limit = 20, offset = 0, authorization = get_spotify_access_token()){
    url <- "https://api.spotify.com/v1/albums"
    parameters <- list(
        ids = paste(ids, collapse = ","),
        market = "US",
        limit = limit,
        offset = offset,
        access_token = authorization
    )
    result = httr::RETRY(verb = "GET", url, query = parameters, encode = "json", terminate_on = c(401, 403, 404))
    httr::stop_for_status(result)
    result <- jsonlite::fromJSON(httr::content(result, as = "text", encoding = "UTF-8"), flatten = TRUE)
    result$artists <- purrr::map(result$artists, ~ list(id = .x$id, name = .x$name))
    result <- result$albums$tracks.items %>%
            purrr::map_df(as.data.frame) %>%
            dplyr::mutate(
                artist_id = purrr::map_chr(artists, ~ toString(.x$id)),
                artist_name = purrr::map_chr(artists, ~ toString(.x$name))
                ) %>%
            dplyr::select(-href,
            -preview_url,
            -uri,
            -external_urls.spotify,
            -is_local,
            -artists,
            -is_playable) %>%
            dplyr::rename(
                track_id = id,
                track_name = name
            )
    result
}
```

Parameters:
    ids - A vector of Spotify track ids
    authorization - access_token generated from the get_spotify_access_token() function
Return:
    A dataframe of track information, including duration, explicitness, track name and id, popularity, whether the song was in an album or a single, album name and id, release date, number of tracks on album, and artist name and id

```{r | new get_tracks function}
get_tracks <- function(ids, authorization = get_spotify_access_token()){
    url <- "https://api.spotify.com/v1/tracks"
    parameters <- list(
    market = "US",
    access_token = authorization
    )
    if (length(ids) > 1) {
        # For multiple IDs
        param <- list(
            ids = paste(ids, collapse = ",")
    )
        parameters <- c(parameters, param)
    } else {
        # For single ID
        url <- stringr::str_glue("{url}/{ids}")
    }
    result = httr::RETRY(verb = "GET", url, query = parameters, encode = "json", terminate_on = c(401, 403, 404))
    httr::stop_for_status(result)
    result <- jsonlite::fromJSON(httr::content(result, as = "text", encoding = "UTF-8"), flatten = TRUE)
    if (length(ids) > 1) {
    # For multiple IDs
        result <- result$tracks
        result$artists <- purrr::map(result$artists, ~ list(id = .x$id, name = .x$name))
        result <- result %>%
      dplyr::mutate(
        artist_id = purrr::map_chr(artists, ~ toString(.x$id)),
        artist_name = purrr::map_chr(artists, ~ toString(.x$name))
      ) %>%
      dplyr::select(
        -is_playable,
        -album.is_playable,
        -href,
        -is_local,
        -preview_url,
        -uri,
        -album.artists,
        -album.href,
        -album.type,
        -album.uri,
        -album.external_urls.spotify,
        -external_ids.isrc,
        -external_urls.spotify,
        -album.images,
        -artists
      ) %>%
      dplyr::rename(
        album_type = album.album_type,
        track_name = name,
        track_id = id,
        album_name = album.name,
        album_id = album.id
      )
  } else {
    # For single ID
        df <- data.frame(
        disc_number = result$disc_number,
        duration_ms = result$duration_ms,
        explicit = result$explicit,
        track_id = result$id,
        track_name = result$name,
        popularity = result$popularity,
        album_type = result$album$album_type,
        album_name = result$album$name,
        album.release_date = result$album$release_date,
        album.release_date_precision = result$album$release_date_precision,
        album.total_tracks = result$album$total_tracks,
        artist_id = paste(result$artist$id, collapse = ", "),
        artist_name = paste(result$artist$name, collapse = ", ")
        )
    result <- df
  }
  result
}
```

Parameters:
    ids - A vector of Spotify track ids
    authorization - access_token generated from the get_spotify_access_token() function
Return:
    A dataframe of track feature information, including track id and the following variables:
        danceability
        energy
        key
        loudness
        mode
        speechiness
        acousticness
        instrumentalness
        liveness
        valence
        tempo
        duration_ms
        time_signature

```{r | new get_track_audio_features function}
get_track_audio_features <- function(ids, authorization = get_spotify_access_token()){
    assertthat::assert_that(
        length(ids) <= 100,
        msg = "The maximum length of the length of the ids vector is 100.  Please shorten the length of the inputed vector."
    )
    url <- 'https://api.spotify.com/v1/audio-features'
    parameters <- list(
        ids = paste0(ids, collapse = ','),
        access_token = authorization
    )
    result <- httr::RETRY('GET', url, query = parameters, encode = 'json')
    httr::stop_for_status(result)

    result <- jsonlite::fromJSON(httr::content(result, as = 'text', encoding = 'UTF-8'), flatten = TRUE)
    result <- result$audio_features %>% 
    dplyr::select(
        -type,
        -uri,
        -track_href,
        -analysis_url
    ) %>%
    dplyr::rename(
        track_id = id
    )

    result
}
```

Parameters:
    id - A single Spotify track id
    authorization - access_token generated from the get_spotify_access_token() function
Return:
    A list of audio analysis data, including meta, track, bars, beats, sections, tatums, and segments data

```{r | new get_track_audio_analysis}
get_track_audio_analysis <- function(id, authorization = get_spotify_access_token()){
    url <- stringr::str_glue("https://api.spotify.com/v1/audio-analysis/{id}")

    parameters <- list(
        access_token = authorization
    )
    result <- httr::RETRY('GET', url, query = parameters, encode = 'json', terminate_on = c(401, 403, 404))
    httr::stop_for_status(result)

    result <- jsonlite::fromJSON(httr::content(result, as = 'text', encoding = 'UTF-8'), flatten = TRUE)

    result
}
```

Parameters:
    id - A single Spotify track id
    authorization - access_token generated from the get_spotify_access_token() function
Return:
    A dataframe of track data, including track id, duration, loudness, start and end of fade, tempo and confidence, time signature and confidence, key and confidence, and mode and confidence

```{r | new get_track_analysis}
get_track_analysis <- function(id, authorization = get_spotify_access_token()){
    result <- as.data.frame(get_track_audio_analysis(id, authorization = authorization)$track) %>%
              dplyr::select(-sample_md5,
                     -codestring,
                     -code_version,
                     -echoprintstring,
                     -echoprint_version,
                     -synchstring,
                     -synch_version,
                     -rhythmstring)
    track_id <- data.frame(track_id = id)
    result <- merge(track_id, result)
    result
}
```

Parameters:
    id - A single Spotify track id
    authorization - access_token generated from the get_spotify_access_token() function
Return:
    A dataframe of track bar information, including track id, and start, end, and confidence of bar intervals

```{r | new get_track_bars}
get_track_bars <- function(id, authorization = get_spotify_access_token()){
    result <- as.data.frame(get_track_audio_analysis(id, authorization = authorization)$bars)
    track_id <- data.frame(track_id = id)
    result <- merge(track_id, result)
    result
}
```

Parameters:
    id - A single Spotify track id
    authorization - access_token generated from the get_spotify_access_token() function
Return:
    A dataframe of track beat information, including track id, and start, end, and confidence of beat intervals

```{r | new get_track_beats}
get_track_beats <- function(id, authorization = get_spotify_access_token()){
    result <- as.data.frame(get_track_audio_analysis(id, authorization = authorization)$beats)
    track_id <- data.frame(track_id = id)
    result <- merge(track_id, result)
    result
}
```

Parameters:
    id - A single Spotify track id
    authorization - access_token generated from the get_spotify_access_token() function
Return:
    A dataframe of track section information, including track id, start, end, and confidence of section intervals, loudness, tempo and confidence, key and confidence, mode and confidence, and time signature and confidence

```{r | new get_track_sections}
get_track_sections <- function(id, authorization = get_spotify_access_token()){
    result <- as.data.frame(get_track_audio_analysis(id, authorization = authorization)$sections)
    track_id <- data.frame(track_id = id)
    result <- merge(track_id, result)
    result
}
```

Parameters:
    id - A single Spotify track id
    authorization - access_token generated from the get_spotify_access_token() function
Return:
    A dataframe of track tatum information, including track id, and start, end, and confidence of tatum intervals

```{r | new get_track_tatums}
get_track_tatums <- function(id, authorization = get_spotify_access_token()){
    result <- as.data.frame(get_track_audio_analysis(id, authorization = authorization)$tatums)
    track_id <- data.frame(track_id = id)
    result <- merge(track_id, result)
    result
}
```

Parameters:
    id - A single Spotify track id
    authorization - access_token generated from the get_spotify_access_token() function
Return:
    A dataframe of track segment information, including track id, start, end, and confidence of segment intervals, loudness at the start of the interval, time of maximum loudness, the maximum loudness, the end loudness, the pitches, and the timbre

```{r | new get_track_segments}
get_track_segments <- function(id, authorization = get_spotify_access_token()){
    result <- as.data.frame(get_track_audio_analysis(id, authorization = authorization)$segments)
    track_id <- data.frame(track_id = id)
    result <- merge(track_id, result)
    result
}
```

Parameters:
    id - A single Spotify artist id
    authorization - access_token generated from the get_spotify_access_token() function
Return:
    A dataframe of album track data, including ids and names for the tracks, whether the track is explicit, track number in the album, artist names and ids, and the following variables:
        danceability
        energy
        key
        loudness
        mode
        speechiness
        acousticness
        instrumentalness
        liveness
        valence
        tempo
        duration_ms
        time_signature

```{r | new get_genre_track_features}
get_album_track_features <- function(id, authorization = get_spotify_access_token()){
    tracks <- get_albums_tracks(id, authorization = authorization)

    features <- get_track_audio_features(tracks$track_id, authorization = authorization)

    result <- dplyr::left_join(tracks, features, by = "track_id") %>%
              dplyr::select(
                -duration_ms.x,
                -is_playable,
                -disc_number
              ) %>%
              dplyr::rename(
                duration_ms = duration_ms.y,
                track_name = name
              )

    result
}
```

Parameters:
    id - A single Spotify artist id
    authorization - access_token generated from the get_spotify_access_token() function
Return:
    A dataframe of track data, including the duration, track id and name, explicitness, popularity, track number in its album, album name and id, and artist name and id

```{r | new get_artist_top_tracks}
get_artist_top_tracks <- function(id, authorization = get_spotify_access_token()){
    url <- stringr::str_glue("https://api.spotify.com/v1/artists/{id}/top-tracks")
    parameters = list(
        market = "US",
        access_token = authorization
    )
    result <- httr::RETRY(verb = 'GET', url, query = parameters, encode = 'json', terminate_on = c(401, 403, 404))
    httr::stop_for_status(result)
    result$artists <- purrr::map(result$artists, ~ list(id = .x$id, name = .x$name))
    result <- jsonlite::fromJSON(httr::content(result, as = 'text', encoding = 'UTF-8'), flatten = TRUE)$tracks %>%
              dplyr::mutate(
                artist_id = purrr::map_chr(artists, ~ toString(.x$id)),
                artist_name = purrr::map_chr(artists, ~ toString(.x$name))
                ) %>%
              dplyr::select(
                -href,
                -is_local,
                -is_playable,
                -preview_url,
                -uri,
                -album.artists,
                -album.href,
                -album.images,
                -album.is_playable,
                -album.release_date,
                -album.release_date_precision,
                -album.total_tracks,
                -album.type,
                -album.uri,
                -album.external_urls.spotify,
                -external_ids.isrc,
                -external_urls.spotify,
                -artists
                ) %>%
              dplyr::rename(
                track_id = id,
                album_type = album.album_type,
                album_name = album.name,
                track_name = name,
                album_id = album.id
              )

    result
}
```